---
title: "Lilly Trulicity Innovid Log Level Pathing Analysis"
output: html_notebook
---
### Preparation: Global setup #####################################################################################################################
```{r setup, include=FALSE}
rm(list=ls())
gc(reset = TRUE)
options(scipen = 999)
library(RJDBC)
library(data.table)
library(ggplot2)
```
### Preparation: Connection to Redshift ######################################################################################################
```{r}
### Connect to Redshift
redshift_jdbc_driver <- "~/Docs/Software/RedshiftJDBC42-no-awssdk-1.2.47.1071.jar"
creds <- fread("~/Docs/Codes/creds.param")
drv <- JDBC("com.amazon.redshift.jdbc42.Driver", redshift_jdbc_driver, identifier.quote="`")
connr <- dbConnect(drv, creds$url[1], creds$un[1], creds$pw[1])
tmp_path <- '~/Docs/Output/Temp/'
```
### Formatting the data and append attributes ######################################################################################################
```{r}
dbSendUpdate(connr, "drop table if exists ca.yj_innovid_cookie_data_formatted")
print(Sys.time())
dbSendUpdate(connr, "
create table ca.yj_innovid_cookie_data_formatted as
select t1.cookieid, t1.eventtime as eventtime, t1.placement_key, t4.placement_name as placement, uniteventsname, postalcode, t1.dma_key as dma, t1.campaign_key,
t2.campaign_name as campaign, client, t1.publisher_key, t5.publisher_name as publisher, t1.creative_key, t3.creative_name as creativename, format, duration, t6.dma_name as dmaname, unitevents, impressions, clickthroughs, completion25, completion50, completion75, completion100, awareness
FROM ca.innovid_log_level as t1 left join ca.innovid_campaign as t2
on t1.campaign_key = t2.campaign_key
left join ca.innovid_creative as t3
on t1.creative_key = t3.creative_key
left join ca.innovid_placement as t4
on t1.placement_key = t4.placement_key
left join ca.innovid_publisher as t5
on t1.publisher_key = t5.publisher_key
left join ca.innovid_dma as t6
on t1.dma_key = t6.dma_key
where lower(t2.campaign_name) like '%trulicity%'
")
print(Sys.time())
dbGetQuery(connr, "select count(1), count(distinct cookieid) from ca.yj_innovid_cookie_data_formatted")
print(Sys.time())
dbGetQuery(connr, "select count(1), count(distinct cookieid) from ca.yj_innovid_cookie_data_formatted where not (cookieid in ('null', '-1', '-2'))")
print(Sys.time())
```
### (Pathing Analysis Deck Slide 3) Extract data for EDA analysis 
```{sql connection=connr, output.var = "imp_by_date"}
SELECT trunc(eventtime) as date1, 
case when lower(campaign) like '%trulicity%' then 1 else 0 end as c1,
count(1) as cnt, count(distinct cookieid) as cnt_id, sum(impressions) as impressions, sum(clickthroughs) as clickthroughs, 
sum(completion25) as completion25, sum(completion50) as completion50, sum(completion75) as completion75, sum(completion100) as completion100, sum(awareness) as awareness 
FROM ca.yj_innovid_cookie_data_formatted
group by 1, 2
order by 1, 2
limit 1000
```
```{r}
fwrite(imp_by_date, paste0(tmp_path,"output1.csv"))
```

### (Pathing Analysis Deck Slide 5 - 6) Extract data for EDA analysis ######################################################################################################
```{sql connection=connr}
select case when lower(campaign) like '%trulicity%' then 1 else 0 end as c1,
publisher, format, duration, sum(impressions) as impressions, sum(clickthroughs) as clickthroughs, sum(completion100) as completion100
from ca.yj_innovid_cookie_data_formatted
group by 1, 2, 3, 4
order by 1, 2, 3, 4
limit 10;
```
###  (Pathing Analysis Deck Slide 5 - 6) 
```{sql connection=connr, output.var = "placement_summary"}
select case when lower(campaign) like '%trulicity%' then 1 else 0 end as c1, placement, sum(impressions) as impressions, sum(clickthroughs) as clickthroughs, sum(completion100) as completion100, sum(awareness) as awarenessss
from ca.yj_innovid_cookie_data_formatted
group by 1, 2
order by 1, 2;
```
```{r}
fwrite(placement_summary, paste0(tmp_path, "invd_placement_summary.csv"))
```

### (Pathing Analysis Deck Slide 4) 
```{sql connection=connr}
select case when lower(campaign) like '%trulicity%' then 1 else 0 end as c1,
dmaname, sum(impressions) as impressions, sum(clickthroughs) as clickthroughs, sum(completion100) as completion100
from ca.yj_innovid_cookie_data_formatted
group by 1, 2
order by 1, 2
limit 10;
```
### Append KPI to impressions ######################################################################################################
```{r}
# dbSendUpdate(connr, "drop table if exists ca_adhoc_view.yj_invd_imp_kpi_nonnull")
print(Sys.time())
dbSendUpdate(connr, "
create table ca_adhoc_view.yj_invd_imp_kpi_nonnull as
select t1.cookieid, t1.eventtime as eventtime_imp, t1.placement, t1.creative_key, t1.dma, t1.uniteventsname, t1.postalcode,
t1.campaign, t1.client, t1.publisher, t1.creativename, t1.format, t1.duration, t1.dmaname, t1.unitevents, t1.impressions,
case when (t2.eventtime >= t1.eventtime) then t2.eventtime else null end as eventtime_click,
case when (t2.eventtime >= t1.eventtime) then t2.clickthroughs else 0 end as clickthroughs,
case when (t6.eventtime >= t1.eventtime) then t6.eventtime else null end as eventtime_completion100,
case when (t6.eventtime >= t1.eventtime) then t6.completion100 else 0 end as completion100
from 
(select * from ca.yj_innovid_cookie_data_formatted where impressions > 0 and not (cookieid in ('null', '-1', '-2'))) as t1
left join (select * from ca.yj_innovid_cookie_data_formatted where clickthroughs > 0) as t2
on t1.cookieid = t2.cookieid and t1.placement_key = t2.placement_key and t1.creative_key = t2.creative_key and t1.dma = t2.dma and t1.postalcode = t2.postalcode
left join (select * from ca.yj_innovid_cookie_data_formatted where completion100 > 0) as t6
on t1.cookieid = t6.cookieid and t1.placement_key = t6.placement_key and t1.creative_key = t6.creative_key and t1.dma = t6.dma and t1.postalcode = t6.postalcode
")
print(Sys.time())
# 1h 45m 49.9s
# if keeping null ids, 5h 46m 16.4s
dbGetQuery(connr, "select count(1), count(distinct cookieid) from ca_adhoc_view.yj_invd_imp_kpi_nonnull")
print(Sys.time())
```
### Aggregate to the unique clicks ######################################################################################################
```{r}
# dbSendUpdate(connr, "drop table if exists ca_adhoc_view.yj_invd_imp_dsct_kpi")
print(Sys.time())
dbSendUpdate(connr, "
create table ca_adhoc_view.yj_invd_imp_dsct_kpi as
select cookieid, eventtime_imp, placement, creative_key, dma, uniteventsname, postalcode, campaign, publisher, creativename, format, duration,
min(eventtime_click) as eventtime_click, min(eventtime_completion100) as eventtime_completion100,
sum(clickthroughs) as clickthroughs, sum(completion100) as completion100
from ca_adhoc_view.yj_invd_imp_kpi_nonnull
group by cookieid, eventtime_imp, placement, creative_key, dma, uniteventsname, postalcode, campaign, publisher, creativename, format, duration
")
print(Sys.time())
# 25m 7.25s
dbGetQuery(connr, "select count(1), count(distinct cookieid) from ca_adhoc_view.yj_invd_imp_dsct_kpi")
print(Sys.time())
```
### Rank ordering the impressions ######################################################################################################
```{r}
dbSendUpdate(connr, "drop table ca_adhoc_view.yj_invd_imp_order")
print(Sys.time())
dbSendUpdate(connr, "
create table ca_adhoc_view.yj_invd_imp_order as
select cookieid, eventtime_imp, placement, creative_key, dma, uniteventsname, postalcode, eventtime_click, eventtime_completion100, clickthroughs, completion100, campaign, publisher, creativename, format, duration,
       row_number() over (partition by cookieid order by eventtime_imp) as order_imp
  from ca_adhoc_view.yj_invd_imp_dsct_kpi
")
print(Sys.time())
# 19m 14.51s
dbGetQuery(connr, "select count(1), count(distinct cookieid) from ca_adhoc_view.yj_invd_imp_order")
print(Sys.time())
```
####  (Pathing Analysis Deck Slide 7 & 9) diminishing returns
```{sql connection = connr, output.var = "diminishing_returns"}
select case when clicked_order_imp is not null then clicked_order_imp else order_imp end as order_imp, 
       count(1) as cnt,
       sum(case when clicked_order_imp is not null then 1 else 0 end) as clicked
  from
(select cookieid, 
        first_eventtime, 
        min_imp_with_clk as clicked_order_imp, 
        max(order_imp) as order_imp
   from (select t1.cookieid, 
                case when date_diff('day', t3.first_eventtime, t1.eventtime_imp) < 31 then t1.order_imp else 1 end as order_imp,
                case when date_diff('day', t3.first_eventtime, t2.min_eventtime_with_clk) < 31 then t2.min_imp_with_clk else null end as min_imp_with_clk, 
                t3.first_eventtime
           from ca_adhoc_view.yj_invd_imp_order as t1 
      left join (select cookieid, 
                        min(order_imp) as min_imp_with_clk, 
                        min(eventtime_imp) as min_eventtime_with_clk
                   from ca_adhoc_view.yj_invd_imp_order
                  where clickthroughs > 0
               group by cookieid) as t2
             on t1.cookieid = t2.cookieid
      left join (select cookieid, 
                        min(eventtime_imp) as first_eventtime 
                   from ca_adhoc_view.yj_invd_imp_order 
               group by cookieid) as t3
             on t1.cookieid = t3.cookieid)
group by cookieid, first_eventtime, min_imp_with_clk)
group by 1
order by 1
```
```{r}
fwrite(diminishing_returns, paste0(tmp_path, "diminishing_returns.csv"))
```

####  (Pathing Analysis Deck Slide 9) more exposures after 1st
```{sql connection=connr, output.var="more_exposures"}
select clicked_order_imp, order_imp, count(1) as cnt
from (select cookieid, min_imp_with_clk as clicked_order_imp, max(order_imp) as order_imp
from
(select t1.cookieid, t1.order_imp, t2.min_imp_with_clk
from ca.yj_invd_imp_order as t1 left join
(select cookieid, min(order_imp) as min_imp_with_clk
from ca.yj_invd_imp_order
where clickthroughs > 0
group by cookieid) as t2
on t1.cookieid = t2.cookieid)
group by cookieid, min_imp_with_clk)
where clicked_order_imp is not null
group by 1, 2
order by 1, 2
```
```{r}
fwrite(more_exposures, paste0(tmp_path, "more_exposures_after_1st_click_by_impression_number.csv"))
```

### (Pathing Analysis Deck Slide 8)  Prepare data for 2-imp analysis ######################################################################################################
```{r}
dbSendUpdate(connr, "drop table if exists ca_adhoc_view.yj_invd_2imp")
print(Sys.time())
dbSendUpdate(connr, "
create table ca_adhoc_view.yj_invd_2imp as
select t3.*
from (select distinct cookieid from ca_adhoc_view.yj_invd_imp_order where clickthroughs = 0 and order_imp = 1) as t1,
(select distinct cookieid from ca_adhoc_view.yj_invd_imp_order where order_imp = 2) as t2, ca_adhoc_view.yj_invd_imp_order as t3
where t1.cookieid = t2.cookieid and t1.cookieid = t3.cookieid and t3.order_imp < 3
")
print(Sys.time())
# 8m 39.21s
dbGetQuery(connr, "select count(1), count(distinct cookieid) from ca_adhoc_view.yj_invd_2imp")
print(Sys.time())
```
#### 2 different ads
```{sql connection=connr}
select case when t1.ad1 = t2.ad2 then 'same' else 'different' end as comparison, count(1) as cnt, sum(clickthroughs) as clickthroughs
from (select cookieid, campaign as ad1 from ca_adhoc_view.yj_invd_2imp where order_imp = 1) as t1,
(select cookieid, campaign as ad2, case when clickthroughs > 0 then 1 else 0 end as clickthroughs from ca_adhoc_view.yj_invd_2imp where order_imp = 2) as t2
where t1.cookieid = t2.cookieid
group by 1
```
#### 2 ads in different order
```{sql connection=connr}
select t1.ad1, t2.ad2, count(1) as cnt, sum(clickthroughs) as clickthroughs
from (select cookieid, case when campaign like '%GM%' then 'GM' else 'MCM' end as ad1 from ca_adhoc_view.yj_invd_2imp where order_imp = 1) as t1,
(select cookieid, case when campaign like '%GM%' then 'GM' else 'MCM' end as ad2, case when clickthroughs > 0 then 1 else 0 end as clickthroughs from ca_adhoc_view.yj_invd_2imp where order_imp = 2) as t2
where t1.cookieid = t2.cookieid
group by 1, 2
limit 1000
```
### Aggregate the journey paths with up to the first 5 touchpoints ##########################################################################################
```{r}
dbSendUpdate(connr, "drop table ca_adhoc_view.yj_invd_first5_imp")
print(Sys.time())
dbSendUpdate(connr, "
create table ca_adhoc_view.yj_invd_first5_imp as
select t1.cookieid, 
t1.placement as placement1, t1.campaign as campaign1, t1.publisher as publisher1, t1.creativename as creativename1, t1.format as format1, t1.duration as duration1, case when t1.clickthroughs > 0 then 1 else 0 end as click1,
case when t1.completion100 > 0 then 1 else 0 end as completion100_1, 
t2.placement as placement2, t2.campaign as campaign2, t2.publisher as publisher2, t2.creativename as creativename2, t2.format as format2, t2.duration as duration2, case when t2.clickthroughs > 0 then 1 else 0 end as click2,
case when t2.completion100 > 0 then 1 else 0 end as completion100_2, 
t3.placement as placement3, t3.campaign as campaign3, t3.publisher as publisher3, t3.creativename as creativename3, t3.format as format3, t3.duration as duration3, case when t3.clickthroughs > 0 then 1 else 0 end as click3,
case when t3.completion100 > 0 then 1 else 0 end as completion100_3, 
t4.placement as placement4, t4.campaign as campaign4, t4.publisher as publisher4, t4.creativename as creativename4, t4.format as format4, t4.duration as duration4, case when t4.clickthroughs > 0 then 1 else 0 end as click4,
case when t4.completion100 > 0 then 1 else 0 end as completion100_4, 
t5.placement as placement5, t5.campaign as campaign5, t5.publisher as publisher5, t5.creativename as creativename5, t5.format as format5, t5.duration as duration5, case when t5.clickthroughs > 0 then 1 else 0 end as click5,
case when t5.completion100 > 0 then 1 else 0 end as completion100_5, 
t6.maxclick, maxcompletion100
from 
(select * from ca_adhoc_view.yj_invd_imp_order where order_imp = 1) as t1
left join
(select * from ca_adhoc_view.yj_invd_imp_order where order_imp = 2) as t2
on t1.cookieid = t2.cookieid
left join
(select * from ca_adhoc_view.yj_invd_imp_order where order_imp = 3) as t3
on t1.cookieid = t3.cookieid
left join
(select * from ca_adhoc_view.yj_invd_imp_order where order_imp = 4) as t4
on t1.cookieid = t4.cookieid
left join
(select * from ca_adhoc_view.yj_invd_imp_order where order_imp = 5) as t5
on t1.cookieid = t5.cookieid
left join
(select cookieid, max(clickthroughs) as maxclick, max(completion100) as maxcompletion100 
from ca_adhoc_view.yj_invd_imp_order group by cookieid) as t6
on t1.cookieid = t6.cookieid
")
print(Sys.time())
# 4m 22.01s
dbGetQuery(connr, "select count(1), count(distinct cookieid) from ca_adhoc_view.yj_invd_first5_imp")
print(Sys.time())
```
```{r}
dbSendUpdate(connr, "drop table if exists ca_adhoc_view.yj_invd_first5_imp_time")
print(Sys.time())
dbSendUpdate(connr, "
create table ca_adhoc_view.yj_invd_first5_imp_time as
select cookieid, case when eventtime_imp2 is not null then date_diff('second', eventtime_imp1, eventtime_imp2) else null end as dif12, 
case when eventtime_imp3 is not null then date_diff('second', eventtime_imp2, eventtime_imp3) else null end as dif23, 
case when eventtime_imp4 is not null then date_diff('second', eventtime_imp3, eventtime_imp4) else null end as dif34, 
case when eventtime_imp5 is not null then date_diff('second', eventtime_imp4, eventtime_imp5) else null end as dif45
from ca_adhoc_view.yj_invd_first5_imp
where eventtime_imp2 is not null
")
print(Sys.time())
dbGetQuery(connr, "select count(1), count(distinct cookieid) from ca_adhoc_view.yj_invd_first5_imp_time")
print(Sys.time())
```
###  (Pathing Analysis Deck Slide 8) Check the ad performance for 2-view paths by video format
```{sql connection=connr}
select format1, format2, count(1) as cnt, sum(click1) as click1, sum(click2) as click2, sum(maxclick) as maxclick
from ca_adhoc_view.yj_invd_first5_imp
where format3 is null and format2 is not null and click1 = 0
group by format1, format2
order by 1, 2
```
### Counting the users per journey path ######################################################################################################
```{r}
dbSendUpdate(connr, "drop table if exists ca_adhoc_view.yj_invd_top_paths")
print(Sys.time())
dbSendUpdate(connr, "
create table ca_adhoc_view.yj_invd_top_paths as
select placement1, campaign1, publisher1, creativename1, click1, completion100_1,
placement2, campaign2, publisher2, creativename2, click2, completion100_2,
placement3, campaign3, publisher3, creativename3, click3, completion100_3,
placement4, campaign4, publisher4, creativename4, click4, completion100_4,
placement5, campaign5, publisher5, creativename5, click5, completion100_5,
count(1) as cnt
from ca_adhoc_view.yj_invd_first5_imp
group by placement1, campaign1, publisher1, creativename1, click1, completion100_1,
placement2, campaign2, publisher2, creativename2, click2, completion100_2,
placement3, campaign3, publisher3, creativename3, click3, completion100_3,
placement4, campaign4, publisher4, creativename4, click4, completion100_4,
placement5, campaign5, publisher5, creativename5, click5, completion100_5
order by count(1) desc
")
print(Sys.time())
# 5m 45.98s
dbGetQuery(connr, "select count(1) from ca_adhoc_view.yj_invd_top_paths")
print(Sys.time())
```
###  (Pathing Analysis Deck Slide 14) Analysis of the time between 2 consecutive impressions.
```{sql connection=connr, output.var="dif12"}
select dif12 from ca_adhoc_view.yj_invd_first5_imp_time where random() < 0.01 and dif12 is not null
```
```{sql connection=connr, output.var="dif45"}
select dif45 from ca_adhoc_view.yj_invd_first5_imp_time where random() < 0.01 and dif45 is not null
```
```{r}
dat_plot2 <- rbind(data.table(grp = 'Imp 1 vs Imp 2', time = dif12$dif12 ), 
                  data.table(grp = 'Imp 4 vs Imp 5', time = dif45$dif45 ))
ggplot(dat_plot2, aes(x = time, group = grp, color = grp)) + geom_density() + scale_x_continuous(lim = c(0, 600)) + xlab("Seconds between two consecutive impressions") + ggtitle("Density of the time between two consecutive impressions") + theme_classic() + theme(legend.position="bottom", text = element_text(size=25))
```
###  (Pathing Analysis Deck Slide 10) Analysis of the top paths
```{sql connection = connr}
select cnt_cookies_nonclick1, cnt_cookies_nonclick1_click2 from
(select sum(cnt) as cnt_cookies_nonclick1 from ca_adhoc_view.yj_invd_top_paths where click1 = 0) as t1, 
(select sum(cnt) as cnt_cookies_nonclick1_click2 from ca_adhoc_view.yj_invd_top_paths where click1 = 0 and click2 = 1) as t2
```
```{sql connection = connr}
select cnt_cookies_nonclick1_click2_ne_cre, cnt_cookies_nonclick1_click2_ne_cam, cnt_cookies_nonclick1_click2_ne_pub, cnt_cookies_nonclick1_click2_ne_pla
from (select sum(cnt) as cnt_cookies_nonclick1_click2_ne_cre 
from ca_adhoc_view.yj_invd_top_paths 
where click1 = 0 and click2 = 1 and creativename1 != creativename2),
(select sum(cnt) as cnt_cookies_nonclick1_click2_ne_cam
from ca_adhoc_view.yj_invd_top_paths 
where click1 = 0 and click2 = 1 and campaign1 != campaign2),
(select sum(cnt) as cnt_cookies_nonclick1_click2_ne_pub
from ca_adhoc_view.yj_invd_top_paths 
where click1 = 0 and click2 = 1 and publisher1 != publisher2),
(select sum(cnt) as cnt_cookies_nonclick1_click2_ne_pla
from ca_adhoc_view.yj_invd_top_paths 
where click1 = 0 and click2 = 1 and placement1 != placement2)
```
```{sql connection = connr, output.var = 'creative1'}
select distinct creativename1
from ca_adhoc_view.yj_invd_top_paths 
where click1 = 0 and click2 = 1 and creativename1 != creativename2
```
```{sql connection = connr}
select case when creativename1 = creativename2 then 'same' else 'different' end as compare_creative, click2, sum(cnt) as cnt
from ca_adhoc_view.yj_invd_top_paths 
where click1 = 0 and creativename2 is not null
group by 1, 2
```
```{sql connection = connr, output.var = 'creative1_nonclick1'}
select case when creativename1 = creativename2 then 'same' else 'different' end as compare_creative, 
creativename1, creativename2, click2, sum(cnt) as cnt
from ca_adhoc_view.yj_invd_top_paths 
where click1 = 0 and creativename2 is not null
group by 1, 2, 3, 4
```

```{sql connection = connr, output.var = 'creative1_nonclick1_sample1'}
select placement1, campaign1, publisher1, click2, sum(cnt) as cnt
from ca_adhoc_view.yj_invd_top_paths
where click1 = 0 and creativename1 = 'Prog_LLTR0084000H_FoodTruck_SPA_60_Innovid'
and creativename2 = 'Prog_LLTR0084000H_FoodTruck_SPA_60_Innovid HTML EV'
and placement3 is null
group by 1, 2, 3, 4
```

```{sql connection = connr}
select case when creativename1 = creativename2 then 'same' else 'different' end as compare_creative, 
creativename1, creativename2, click2, sum(cnt) as cnt
from ca_adhoc_view.yj_invd_top_paths 
where click1 = 0 and creativename1 = 'Prog_LLTR0084000H_FoodTruck_SPA_60_Innovid'
and creativename2 = 'Prog_LLTR0084000H_FoodTruck_SPA_60_Innovid HTML EV'
and placement3 is null
group by 1, 2, 3, 4
```

```{sql connection = connr}
select creativename2, click2, sum(cnt) as cnt
from ca_adhoc_view.yj_invd_top_paths 
where click1 = 0 
and placement1 = 'Trulicity MCM_Video_2020_Accuen_Programmatic_dCPM_Cross Device_Preroll_LAL_TTD_Site Visits_:60_NA'
and campaign1 = 'CY20 - CY20_Q1 - Q4_Diabetes Business Unit_Trulicity_MCM_OLV_ELO_MCM_174'
and publisher1 = 'The Trade Desk'
and creativename1 = 'Prog_LLTR0084000H_FoodTruck_SPA_60_Innovid'
and placement2 = 'Trulicity MCM_Video_2020_Accuen_Programmatic_dCPM_Cross Device_Preroll_LAL_TTD_Site Visits_:60_NA'
and campaign2 = 'CY20 - CY20_Q1 - Q4_Diabetes Business Unit_Trulicity_MCM_OLV_ELO_MCM_174'
and publisher2 = 'The Trade Desk'
and creativename2 in ('Prog_LLTR0084000H_FoodTruck_SPA_60_Innovid', 'Prog_LLTR0084000H_FoodTruck_SPA_60_Innovid HTML EV')
and placement3 is null
group by 1, 2
```
